---
title: "Match_to_broad_cat"
author: "George Batta"
date: '2022-09-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(dplyr)
```




These were obtained from this address, which has monthly files from January 2009 - August 2022:

https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html


pre.tsv gives the line items and associated labels

sub.tsv gives filing and issuer-level information. We restrict to quarterly (10-Q) and annual (10-K) filings, and also exclude financial firms (sic [Standard Industrial Classifiction] between 6000 and 6999)

broad_cat.csv is a categorization file for the tags, which I constructed in `XBRL_preliminary.Rmd`. It includes, at present, the 5 taxonomies from 2018 to 2022, inclusive.

This restricts to 5 categories:

Revenues
Operating Expense
Non-operating items
Interest Expense
Tax Expense

# Initialize parameters to read data

```{r}
# Initialize list of years and quarters
year = 2019:2022
quarter = c("q1", "q2", "q3", "q4")
months = sprintf("%02d", 1:12)

# get current year: data is obtained monthly for current year, (current year - 1) and (current year - 2)
current_year = strtoi(format(Sys.Date(), "%Y"))


```



# Code for Reading files

## Pre files
```{r}
# CODE FOR READING FILES

for(y in year){
  pre <- tibble()
  
  print(c("Year:", y)) #print year in the loop
  
  if(y < current_year - 2){
  
  for(q in quarter){
    assign(paste("pre", "_", y, "_", q, sep = ""),
             as_tibble(read_tsv(paste(getwd(),"/",y, q, "_notes", "/", "pre.tsv", sep = "")))) #assign to dataframe on quarters
    
    # add to tibble
    pre <- bind_rows(pre, get(paste("pre", "_", y, "_", q, sep = "")))
    
    rm(list = paste("pre", "_", y, "_", q, sep = ""))
    
    print(nrow(pre))
  }
    
  }
   else{
     
      for(q in quarter){
    tryCatch({

        assign(paste("pre", "_", y, "_",q, sep = ""), #try assigning on quarters
             as_tibble(read_tsv(paste(getwd(),"/",y, q, "_notes", "/", "pre.tsv", sep = ""))))
      
      # add to tibble
      pre <- bind_rows(pre, get(paste("pre", "_", y, "_", q, sep = "")))
      
      rm(list = paste("pre", "_", y, "_", q, sep = ""))
      
      print(nrow(pre))
      },
        error = function(err){
        print("file not found, trying months") 
    
        use_months <<- TRUE
        
      }
  )

      }
     {
     if(use_months == TRUE){
       for(m in months){
        tryCatch({
          assign(paste("pre", "_", y, "_",m, sep = ""), #or assign on months
                 as_tibble(read_tsv(paste(getwd(),"/",y, "_", m, "_notes", "/", "pre.tsv", sep = ""))))
          
          # add to tibble
          pre <- bind_rows(pre, get(paste("pre", "_", y, "_",m, sep = "")))
          
          rm(list = paste("pre", "_", y, "_",m, sep = ""))
          print(nrow(pre))
        },
        error = function(err2){
          print("file with month not found, trying next")
          
          skip_to_next  <<- TRUE
          
        }
        
      )
         if(skip_to_next == TRUE){ 
          next 
          }
         
       }
     }
  }
   }
  
  write.csv(pre, paste("pre_",y,".csv", sep = ""))
  print(paste("pre_",y,".csv", " is exported", sep = ""))
  
}
```


```{r}
rm(pre)
```


```{r}
#update.packages(checkBuilt=TRUE, ask=FALSE)
```


```{r}
y <- 2019
q <- "q1"
```

```{r}
paste("sub_table", "_", y, "_", q, sep = "")
```
```{r}
read.csv("sub.tsv", sep = "\t")
```

```{r}
read_tsv(paste(getwd(),"/",y, q, "_notes", "/", "sub.tsv", sep = ""))
```



```{r}
 assign(paste("sub_table", "_", y, "_", q, sep = ""),
               as_tibble(read_tsv(paste(getwd(),"/",y, q, "_notes", "/", "sub.tsv", sep = ""))))
```


## Sub Files
```{r}
# CODE FOR READING FILES

for(y in year){
  sub <- tibble()
  
  print(c("Year:", y)) #print year in the loop
  
  if(y < current_year - 2){
  
    for(q in quarter){
      assign(paste("sub", "_", y, "_", q, sep = ""),
               as_tibble(read.csv(paste(getwd(),"/",y, q, "_notes", "/", "sub.tsv", sep = ""), sep = "\t"))) #assign to dataframe on quarters
      
      # add to tibble
      sub <- bind_rows(sub_table, get(paste("sub", "_", y, "_", q, sep = "")))
      
      rm(list = paste("sub", "_", y, "_", q, sep = ""))
      
      print(nrow(sub_table))
    }
    
  }
   else{
     
      for(q in quarter){
    tryCatch({

        assign(paste("sub", "_", y, "_",q, sep = ""), #try assigning on quarters
             as_tibble(read.csv(paste(getwd(),"/",y, q, "_notes", "/", "sub.tsv", sep = ""), sep = "\t")))
      
      # add to tibble
      sub <- bind_rows(sub, get(paste("sub", "_", y, "_", q, sep = "")))
      
      rm(list = paste("sub", "_", y, "_", q, sep = ""))
      
      print(nrow(sub))
      },
        error = function(err){
        print("file not found, trying months") 
    
        use_months <<- TRUE
        
      }
  )

      }
     {
     if(use_months == TRUE){
       for(m in months){
        tryCatch({
          assign(paste("sub", "_", y, "_",m, sep = ""), #or assign on months
                 as_tibble(read.csv(paste(getwd(),"/",y, "_", m, "_notes", "/", "sub.tsv", sep = ""), sep = "\t")))
          
          # add to tibble
          sub <- bind_rows(sub, get(paste("sub", "_", y, "_",m, sep = "")))
          
          rm(list = paste("sub", "_", y, "_",m, sep = ""))
          print(nrow(sub))
        },
        error = function(err2){
          print("file with month not found, trying next")
          
          skip_to_next  <<- TRUE
          
        }
        
      )
         if(skip_to_next == TRUE){ 
          next 
          }
         
       }
     }
  }
   }
  
  write.csv(sub, paste("sub_",y,".csv", sep = ""))
  print(paste("sub_",y,".csv", " is exported", sep = ""))
 
}
```



# Cleaning and Joining


```{r}
# Read broad cat
broad_cat<-as_tibble(read_csv('broad_cat_with_aggregation_v2.csv'))

# Clean and join
for(y in year){
  pre <- as_tibble(read_csv(paste("pre_",y,".csv", sep = "")))
  #tag <- as_tibble(read_tsv('cal.tsv'))
  #txt<- as_tibble(read_tsv('txt.tsv'))
  sub<- as_tibble(read.csv(paste("sub_",y, ".csv", sep = ""))) %>% 
    select(adsh,cik,name,sic,form) %>% 
    filter(form=="10-K" | form=="10-Q") %>% 
    mutate(sic=as.numeric(sic)) %>% 
    filter(sic<6000 | sic>6999)


  assign(paste("df_", y, sep = ""), pre %>% filter(stmt=="IS",!is.na(prole),!str_detect(plabel,"]"),
                        !str_detect(tag,"Abstract$")) %>% 
    arrange(adsh,report,line) %>% inner_join(sub) %>% arrange(desc(tag)) %>% 
    # group_by(tag) %>%  summarize(n=n()) %>% 
    inner_join(broad_cat)  )
  
  #write csv
  write_csv(get(paste("df_", y, sep = "")),paste("df_", y, ".csv", sep = ""))
  
  #cognate search
  assign(paste("cognate_search_", y, sep = ""), eval(as.name(paste("df_", y, sep = ""))) %>% 
    group_by(tag,broad_cat,plabel) %>% 
    summarize(n=n()) %>% ungroup() %>% group_by(tag) %>% 
    mutate(big_n=sum(n)) %>% ungroup() %>% 
    arrange(desc(big_n),desc(n)) %>% select(-big_n))
  
  #export
  write_csv(get(paste("cognate_search_", y, sep = "")),paste("cognate_search_", y, ".csv", sep = ""))

  
}
```
The code generates dataframes for each year.
Further joining and analysis is done in Python

